### 2015-01-01 paper_10_intro.tex
adding some data mining for software engineering data
updating some history of software analytics

\subsubsection{SOFTWARE ANALYTICS}
One area of research that is focusing on the evaluation of software development organizations
is \textit{software analytics}.  It is less focused o evaluation
and more so on analysis of software data.  The goal of software analytics is to extract insights
from software artifacts to aide practioners in making better decisions regarding software
development \cite{Zhang2013}.  The main focus areas of software analytics are:
\begin{description}
    \item[User Experience] - How can the software enable the user to more easily or quickly 
        accomplish the task at hand?
    \item[Quality] - How can the number of problems with the software be decreased?
    \item[Development Productivity] - How can the processes or tools be modified to increase 
        the rate at which software is produced? 
\end{description}

@@

See also \cite{Buse2010}.

>>>>

\subsubsection{SOFTWARE ANALYTICS}
The application of data mining techniques to software engineering can be traced back to the
late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.

One area of research that is focusing on the evaluation of software development organizations
is \textit{software analytics}.  It is less focused on evaluation
and more so on all sorts of analysis of software data.  Early forms of 
software analytics were methods of data mining applied to software engineering data
\cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. The term software intelligence was 
used \cite{Hassan2010}, but
the term software analytics has become the common term for referring to the topic \cite{Zhang2011}.
The goal of software analytics is to extract insights
from software artifacts to aide practioners in making better decisions regarding software
development \cite{Zhang2013}.  The main focus areas of software analytics are:
\begin{description}
    \item[User Experience] - How can the software enable the user to more easily or quickly 
        accomplish the task at hand?
    \item[Quality] - How can the number of problems with the software be decreased?
    \item[Development Productivity] - How can the processes or tools be modified to increase 
        the rate at which software is produced? 
\end{description}

@@

See also \cite{Buse2010} and then \cite{Buse2012} begins to discuss the 
information that is needed to properly perform software development analytics.
